---
title: "Template for bookdown"
author: "Dereck de Mézquita"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
github-repo: "dereckdemezquita/bk-statistics-probability-with-R"
documentclass: book
output:
  bookdown::gitbook:
      config:
        toc:
          collapse: subsection
          scroll_highlight: yes
          before: null
          after: null
        toolbar:
          position: fixed
        edit: null
        download: null
        search: yes
        fontsettings:
          theme: night
          family: serif
          size: 2
        sharing:
          facebook: yes
          github: yes
          twitter: yes
          linkedin: yes
          weibo: no
          instapaper: no
          vk: yes
          all: ['facebook', 'twitter', 'linkedin', 'weibo', 'instapaper']
  #bookdown::pdf_book: default
bibliography: [bib/citations.bib, bib/packages.bib]
biblio-style: apalike
link-citations: yes
description: "A full statistics and probability with R programming book. Course material and subject matter inspired by traditional courses, all code demonstrations are my own."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 7, fig.height = 7, fig.align = "center")
```

<!-- If you need PDF output, uncomment bookdown::pdf_book above in YAML. You will need a LaTeX installation, e.g., https://yihui.name/tinytex/ -->

# Introduction {#chp:introduction}

This is a simple and basic template for quickly creating working repos that are set to run and start writing a book or large document with R. Feel free to reference the original bookdown documentation for more information on the syntax required to write a bookdown document: [bookdown.org](https://bookdown.org/yihui/bookdown/)

## Session information
 
This book is written in **R-Markdown** with the **bookdown** package.

```{r session-information}
sessionInfo()
```

<!-- ## Automatically build book script -->

```{r build-book, eval=FALSE, include=FALSE, warning=FALSE, message=FALSE}
for (i in 1:100) {
  tryCatch({
    servr::daemon_stop(i)
  }, error = function(e) {
    message("Error: ", e)
  })
}
bookdown::serve_book(dir = ".", output_dir = "_book", preview = TRUE, in_session = TRUE, quiet = TRUE)
```
 
